Why classical mechanics fails

### 2021-08-24 Articles/2021-WhyClassicalMechanicsFails/WhyClassicalMechanicsFails.tex
ClassicalFail: adding a couple of references

We close with the following general remark. Much of the work on the foundations of physics nowadays is geared toward finding the ``true'' objects and rules of nature. \footnote{CITE: papers that propose emergent models of space time, ...} Even in quantum mechanics, a lot of efforts are aimed at finding the true underlying constituents and mechanisms that would explain the quantum world.\footnote{CITE: papers that propose underlying mechanism (e.g. Bohmian approach, GRW)} In this sense, theoretical physics is built bottom-up. We believe this general approach to be problematic.

>>>>

We close with the following general remark. Much of the work on the foundations of physics nowadays is geared toward finding the ``true'' objects and rules of nature.\cite{huggett2013emergent,oriti2009approaches,lee2020model} \footnote{CITE: papers that propose emergent models of space time, ...} Even in quantum mechanics, a lot of efforts are aimed at finding the true underlying constituents and mechanisms that would explain the quantum world.\cite{larsson2014loopholes, ghirardi1986unified, carroll2019something, nikolic2007bohmian}\footnote{CITE: papers that propose underlying mechanism (e.g. Bohmian approach, GRW)} In this sense, theoretical physics is built bottom-up. We believe this general approach to be problematic.
